### 2014-07-09 tex/main-body-text.tex
Comment out Figure 2.
We hadn't actually referenced it in the main text and I feel
like the paper might be long enough already.  We have it there
in case a referee wants us to put it back in.
Partial edits to conclusion.

\begin{figure}
\begin{center}
	% NOTE. Pat replaced old Q-val-StrFloc.pdf with a ggplot version 
 \includegraphics[width=\columnwidth]{images/Figures-Pat/Fig2.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for $K=5$. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{fig:qscatter}
\end{center}
\end{figure}

@@

One of the major claimed advantages of {\sc flock} over other methods for genetic clustering
is that, ``The very short processing times for each run of {\sc flock} allows for
comparing partitions from many runs of each $K$'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed faster processing times (relative to other methods) in their 
comparisons, we did not observe the same advantage in our analysis. This appears to result from two issues. First,
our example data set was an order of magnitude larger than the largest data set analyzed in \citet{Duc&Tur2012}.  Second, 
in the comparison by \citet{Duc&Tur2012}, 
{\sc flock} was set to perform 50 runs and 20 iterations for each $K$ from 1 to four more than 
the true value of $K$, and computing times for that analysis were compared to times for ten iterations of {\sc structure} using 
a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of $K$ from 1 to three more than the true 
value of $K$. 
To us it seemed reasonable to compare, for each $K$, one iteration of {\sc structure} (50,000 burn in and 200,000 sample collection sweeps)
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both are used to provide a single estimate of the partition of individuals into clusters. One could
argue that it would be more appropriate to compare the running times of the programs according to the number
of opportunities that each individual's cluster membership has for random initialization and reallocation.  Under 
such a perspective, {\sc flock}'s 50 different starting allocations and 20 reallocations should be compared to
50 separate runs of structure, each of length 20 sweeps, which would surely give {\sc structure}
an apparent advantage in speed.  Regardless, while it may hold that {\sc flock}
is able to process small datasets quickly enough to compete with {\sc structure},
the rapid increase in our ability to economically
genotype a large number of individuals for a great many number of loci, may render this advantage less relevant to many 
study designs in the future.

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate K may be overly stringent. While there has been ample 
discourse concering the choice of the optimal K in {\sc structure} \citep{Evannoetal2005, 
Pritchardetal2000, Wap&Gag2006} much less effort has been put forth examining how the number of individuals
and the number of starting allocations can affect not only the convergence of different runs, but also the 
inference of $K$. The authors developed estimation rules based on simulated data 
sets with a modest number of individuals and different migration regimes and rates, number of loci, and K. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular $K$,  similar but not idential 
allocations will provide no support to a given $K$. We highly advise, if using {\sc flock}, to
run multiple small batches and using the programs {\sc clumpp} \citep{Jak&Ros2007} and
{\sc district} \citep{Rosenberg2004} to visually inspect the 'best run' results.

>>>>

%\begin{figure}
%\begin{center}
% \includegraphics[width=\columnwidth]{images/Figures-Pat/Fig2.pdf}
%    \caption{Individual \textit{$q_i$} values plotted for each cluster for $K=5$. 
%{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
% attributed to them.}
%    \label{fig:qscatter}
%\end{center}
%\end{figure}

@@

One of the major claimed advantages of {\sc flock} over other methods for genetic clustering (like {\sc structure})
is that, ``The very short processing times for each run of {\sc flock} allows for
comparing partitions from many runs of each $K$'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed faster processing times (relative to other methods) in their 
comparisons, we did not observe the same advantage in our analysis. This appears to result from two issues. First,
our example data set was an order of magnitude larger than the largest data set analyzed in \citet{Duc&Tur2012}.  Second, 
in the comparison by \citet{Duc&Tur2012}, 
{\sc flock} was set to perform 50 runs and 20 iterations for each $K$ from 1 to four more than 
the true value of $K$, and computing times for that analysis were compared to times for ten iterations of {\sc structure} using 
a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of $K$ from 1 to three more than the true 
value of $K$. 
To us it seemed reasonable to compare, for each $K$, one iteration of {\sc structure} (50,000 burn in and 200,000 sample collection sweeps)
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both are used to provide a single estimate of the partition of individuals into clusters. One could
argue that it would be more appropriate to compare the running times of the programs according to the number
of opportunities that each individual's cluster membership has for random initialization and reallocation.  Under 
such a perspective, {\sc flock}'s 50 different starting allocations and 20 reallocations should be compared to
50 separate runs of structure, each of length 20 sweeps, which would surely give {\sc structure}
an apparent advantage in speed.  Regardless, while it may hold that {\sc flock}
is able to process small datasets quickly enough to compete with {\sc structure},
the rapid increase in our ability to economically
genotype a large number of individuals for a great many loci, may render this advantage less relevant to many 
study designs in the future.

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate $K$ may be overly stringent. While there has been lengthy 
discourse over the choice of estimators for $K$ in {\sc structure} \citep{Pritchardetal2000,Evannoetal2005,Wap&Gag2006,Gaoetal2011} much less effort has been put forth examining how the number of individuals
and the number of starting allocations can affect not only the convergence of different runs of {\sc flock}, but also its 
inference of $K$. The authors developed estimation rules based on simulated data 
sets with a modest number of individuals and different migration regimes and rates, number of loci, and $K$. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular $K$,  similar---but not identical---allocations
will provide no support to a given $K$. If using {\sc flock}, we advise running
multiple small batches and using the programs {\sc clumpp} \citep{Jak&Ros2007} and
{\sc distruct} \citep{Rosenberg2004} to visually inspect the ``best run'' results.
